NEED TITLE

### 2014-09-18 ms.tex
added analytic expectations

%\documentstyle[emulateapj,apjfonts,epsfig]{article}
\documentclass{emulateapj}
%\documentclass[12pt,preprint]{aastex}
%\usepackage{emulateapj5,apjfonts}

\newcommand{\EXO}{\mbox{EXO 0748-676}}
\newcommand{\keV}{${\rm keV}$}
\newcommand{\Fe}{${\rm Fe} \ $}
\newcommand{\Mn}{${\rm Mn} \ $}
\newcommand{\Cr}{${\rm Cr} \ $}
\newcommand{\V}{${\rm V} \ $}
\newcommand{\Ti}{${\rm Ti} \ $}
\newcommand{\Sc}{${\rm Sc} \ $}
\newcommand{\Ca}{${\rm Ca} \ $}

@@

\section{Analytic Expectations}
\section{Comparison with Numerical Results}

@@

What plots should we show?
-density vs r
-velocities vs r
-angular momentum vs r
-mass vs r

>>>>

%\documentstyle[emulateapj,apjfonts,epsfig]{article}
\documentclass{emulateapj}
\usepackage{amsmath, mathtools}

%\documentclass[12pt,preprint]{aastex}
%\usepackage{emulateapj5,apjfonts}

\newcommand{\EXO}{\mbox{EXO 0748-676}}
\newcommand{\keV}{${\rm keV}$}
\newcommand{\Fe}{${\rm Fe} \ $}
\newcommand{\Mn}{${\rm Mn} \ $}
\newcommand{\Cr}{${\rm Cr} \ $}
\newcommand{\V}{${\rm V} \ $}
\newcommand{\Ti}{${\rm Ti} \ $}
\newcommand{\Sc}{${\rm Sc} \ $}
\newcommand{\Ca}{${\rm Ca} \ $}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand       \etaeff       {\eta}
\newcommand       \tff          {\tau_{\rm ff}}
\newcommand       \tdyn         {\tau_{\rm dyn}}

@@

\section{Analytic Expectations}

Recently, Murray \& Chang (2014) considered the spherical collapse of isothermal turbulently supported gas accounting for adiabatic heating from compression of the turbulence. In particular,  {\bf SHOW EQUATIONS}
Their basic results are that the run of density asymptotes to 
\be
\rho(r,t)=
\begin{dcases}
\rho(r_0)\left({r\over r_0}\right)^{-3/2}, & r<r_*\\
\rho(R,t)\left({r\over R}\right)^{-k_\rho}, \ k_\rho\approx1.6-1.8 & r>r_*.
\end{dcases}
\ee
Since $k_\rho$ is fairly close to $1.5$ at all radii, taking $r_0=R$
is a fair approximation. 
The infall velocity 
%
\be
u_r(r,t)=
\begin{dcases}
-\Gamma\sqrt{GM_*(t)\over r}, \sim r^{-1/2} & r<r_*\\
-\Gamma\sqrt{GM(r,t)\over r} \sim r^{0.2} & r>r_*,
\end{dcases}
\ee
%
where $\Gamma \approx 0.7$ at small radii, and $\Gamma\approx 1.0$ at
large radii.

The turbulent velocity 
%
\be
v_T(r,t)=
\begin{dcases}
{1\over 2\etaeff}\Gamma\sqrt{GM_*(t)\over r}, \sim r^{-1/2} & r<r_*\\
{1.2\over \etaeff}\Gamma\sqrt{GM(r,t)\over r} \sim r^{0.2} & r>r_*,
\end{dcases}
\ee
%

The stellar mass increases quadratically with time
%
\be  %$
M_*(t)=\phi M_{\rm cl}\left({t-t_*\over \tff}\right)^2.
\ee  %$
%

The mass accretion rate 
%
\be
\dot M(r,t)=
\begin{dcases}
4\pi R^2\rho(R)u_r(r,t), \sim t\,r^{0} & r<r_*\\
4\pi R^2\rho(R)u_r(r,t) \sim t^0\,r^{0.2} & r>r_*.
\end{dcases}
\ee
%

\section{Numerical Results}

@@

What plots should we show?
-density vs r
-velocities vs r
-angular momentum vs r
-mass vs r
-mdot vs r
